### 2016-06-22 paper/numerical_experiments.tex
aaaaahhhhh

We now present the results of solving the inference problem using Algorithm~\ref{alg:refSeries}, for a range of error tolerances. At each iteration, we choose the basis functions with the largest $10\%$ of the error for model refinement. All simulations are run on a single processor. Table~\ref{tab:ref3D} shows ...
%
\begin{table}[h]
\centering
\begin{tabular}{c|c|c|c|c|c}
\multirow{2}{*}{Case} & \multirow{2}{*}{$\%HF$} & \multirow{2}{*}{QoI} & Relative Error & Relative Error & \multirow{2}{*}{Time (s)} \\ 
& & & (Estimated) & (Actual) & \\ \hline
LF & 0 & 1068856 &  &  &  \\
MF01 & 16.7 &  &  &  &  \\
MF02 & 29.0 &  &  &  &  \\
MF03 & 42.3 &  &  &  &  \\
HF & 100 & 547420 &  &  &  \\
\end{tabular}
\caption{table of things}
\end{table}

>>>>

We now present the results of solving the inference problem using Algorithm~\ref{alg:refSeries}, with a relative error tolerance of $0.1\%$. At each iteration, we choose the basis functions with the largest $10\%$ of the error for model refinement. All simulations are run on a single processor. Table~\ref{tab:ref3D} shows the runtime and error at the end of each iteration. For the high-fidelity inverse problem, the Newton solver does not converge with the initial guess $u=5$, $z=q=0$; instead, we solve the low-fidelity inverse problem and use its solution as the initial guess for the high-fidelity inverse problem. Each iteration of the adaptive algorithm uses the solution of the previous iteration as its initial guess.
%
\begin{table}[h]
\centering
\begin{tabular}{c|c|c|c|c|c}
\multirow{2}{*}{Case} & \multirow{2}{*}{$\%HF$} & \multirow{2}{*}{QoI} & Relative Error & Relative Error & \multirow{2}{*}{Time (s)} \\ 
& & & (Estimated) & (Actual) & \\ \hline
LF & 0 & 1068856 &  &  &  \\
MF01 & 16.7 &  &  &  &  \\
MF02 & 29.0 &  &  &  &  \\
MF03 & 42.3 &  &  &  &  \\
HF & 100 & 547420 &  &  &  \\
\end{tabular}
\caption{table of things}
\end{table}
